Empirical Check of Machine Homogeneity on Timing Protocol

### 2018-05-04 pt_characterization/machine_cons_check/paper.tex
Ricks comment applied

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8} (plugged into \hbox{bottom} {\em left} power strip) & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb9}  (plugged into \hbox{bottom} {\em left} power strip)  &  INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb10}  (plugged into \hbox{bottom} {\em left} power strip)  & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb12}  (plugged into \hbox{bottom} {\em left} power strip)  & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes}}
\end{table}

@@

\newpage

>>>>

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8} (plugged into {\em bottom left} power strip) & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb9}  (plugged into {\em the upper left} power strip)  &  INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb10}  (plugged into {\em the upper left} power strip)  & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
{\tt sodb12}  (plugged into {\em the upper left} power strip)  & INC1$\sim$INC128 & Runs of 300 samples & 2017-02-09 $\sim$ 2017-02-10\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes}}
\end{table}

@@

### 2018-05-04 pt_characterization/machine_cons_check/post_exp.tex
Ricks comment applied

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8} (plugged into \hbox{bottom} {\em left} power strip) &  INC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
{\tt sodb9}  (plugged into \hbox{bottom} {\em left} power strip)  &  IINC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
{\tt sodb10}  (plugged into \hbox{bottom} {\em left} power strip)  & INC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
{\tt sodb12}  (plugged into \hbox{bottom} {\em left} power strip)  & INC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes2}}
\end{table}

@@

>>>>

%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb8} (plugged into {\em bottom left} power strip) &  INC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
{\tt sodb9}  (plugged into {\em the upper left} power strip) &  IINC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
{\tt sodb10} (plugged into {\em the upper left} power strip)  & INC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
{\tt sodb12} (plugged into {\em the upper left} power strip) & INC16, INC13, and INC17.2 & Runs of 1,000 samples & 2018-03-17 $\sim$2018-03-18\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes2}}
\end{table}

@@

\subsection{Intra-Machine Homogeneity~\label{sec:intra_machine}}

A short description of the runs we used for this experiment are exhibited in Table~\ref{tab:exp_notes3}.

%\paragraph{Experimental Notes:} In the experiments 
%we used only {\tt sodb9}. A short summary of the experiments is shown in Table~\ref{tab:exp_notes3}.
%\vspace{-.3in}
%% done
\begin{table}[h]
\begin{center}
\begin{tabular}{|p{4cm}|p{3cm}|p{4cm}|p{4cm}|} \hline
Machine & Task Length & Description & Time Length\\ \hline
{\tt sodb9}  (plugged into {\em the upper left} power strip) &  INC1$\sim$INC128 & Runs of 1,000 samples & 2018-04-28 $\sim$2018-04-30\\ \hline
\end{tabular}
\end{center}
\vspace{-.2in}
\caption{Detailed description of INC data used for histograms\label{tab:exp_notes3}}
\end{table}

%\newpage
%\clearpage

\begin{figure}[H]
	\centering
	\subfigure[PT frequency on INC1 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{new_INC_data_s9/s9_INC1_dist.eps}
		\label{fig:s9_inc1_dist}
	}
	\subfigure[PT frequency on INC2 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{new_INC_data_s9/s9_INC2_dist.eps}
		\label{fig:s9_inc2_dist}
	}
	\subfigure[PT frequency on INC4 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{new_INC_data_s9/s9_INC4_dist.eps}
		\label{fig:s9_inc4_dist}
	}
	\subfigure[PT frequency on INC8 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{new_INC_data_s9/s9_INC8_dist.eps}
		\label{fig:s9_inc8_dist}
	}
	\caption{PT Histograms on INC1$\sim$INC8\label{fig:new_data1}}
\end{figure}

\begin{figure}[h]
	\centering
	\subfigure[PT frequency on INC16 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{new_INC_data_s9/s9_INC16_dist.eps}
		\label{fig:s9_inc16_dist2}
	}
	\subfigure[PT frequency on INC32 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{new_INC_data_s9/s9_INC32_dist.eps}
		\label{fig:s9_inc32_dist}
	}
	\subfigure[PT frequency on INC64 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{new_INC_data_s9/s9_INC64_dist.eps}
		\label{fig:s9_inc64_dist}
	}
	\subfigure[PT frequency on INC128 on {\tt sodb9}]{
		\includegraphics[scale=0.43]{new_INC_data_s9/s9_INC128_dist.eps}
		\label{fig:s9_inc128_dist}
	}
	\caption{PT Histograms on INC16$\sim$INC128\label{fig:new_data2}}
\end{figure}

### 2018-05-04 pt_characterization/machine_cons_check/sodb10/res.tex
Ricks comment applied

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC1]{
		\includegraphics[scale=0.43]{sodb10/1_sec_et_hist_v5.eps}
		\label{fig:s10_inc1_et_hist_v5}
	}
	\subfigure[ET frequency on INC2]{
		\includegraphics[scale=0.43]{sodb10/2_sec_et_hist_v5.eps}
		\label{fig:s10_inc2_et_hist_v5}
	}
	\subfigure[ET frequency on INC4]{
		\includegraphics[scale=0.43]{sodb10/4_sec_et_hist_v5.eps}
		\label{fig:s10_inc4_et_hist_v5}
	}
	\subfigure[ET frequency on INC8]{
		\includegraphics[scale=0.43]{sodb10/8_sec_et_hist_v5.eps}
		\label{fig:s10_inc8_et_hist_v5}
	}
	\caption{ET Histograms of INC1 ... INC8~\label{fig:s10_et_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC16]{
		\includegraphics[scale=0.43]{sodb10/16_sec_et_hist_v5.eps}
		\label{fig:s10_inc16_et_hist_v5}
	}
	\subfigure[ET frequency on INC32]{
		\includegraphics[scale=0.43]{sodb10/32_sec_et_hist_v5.eps}
		\label{fig:s10_inc32_et_hist_v5}
	}
	\subfigure[ET frequency on INC64]{
		\includegraphics[scale=0.43]{sodb10/64_sec_et_hist_v5.eps}
		\label{fig:s10_inc64_et_hist_v5}
	}
	\subfigure[ET frequency on INC128]{
		\includegraphics[scale=0.43]{sodb10/128_sec_et_hist_v5.eps}
		\label{fig:s10_inc128_et_hist_v5}
	}
	\caption{ET Histograms of INC16 ... INC128~\label{fig:s10_et_hist2}}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC1]{
		\includegraphics[scale=0.43]{sodb10/1_sec_pt_hist_v5.eps}
		\label{fig:s10_inc1_hist_v5}
	}
	\subfigure[PT frequency on INC2]{
		\includegraphics[scale=0.43]{sodb10/2_sec_pt_hist_v5.eps}
		\label{fig:s10_inc2_hist_v5}
	}
	\subfigure[PT frequency on INC4]{
		\includegraphics[scale=0.43]{sodb10/4_sec_pt_hist_v5.eps}
		\label{fig:s10_inc4_hist_v5}
	}
	\subfigure[PT frequency on INC8]{
		\includegraphics[scale=0.43]{sodb10/8_sec_pt_hist_v5.eps}
		\label{fig:s10_inc8_hist_v5}
	}
	\caption{PT Histograms of INC1 ... INC8~\label{fig:s10_pt_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC16]{
		\includegraphics[scale=0.43]{sodb10/16_sec_pt_hist_v5.eps}
		\label{fig:s10_inc16_hist_v5}
	}
	\subfigure[PT frequency on INC32]{
		\includegraphics[scale=0.43]{sodb10/32_sec_pt_hist_v5.eps}
		\label{fig:s10_inc32_hist_v5}
	}
	\subfigure[PT frequency on INC64]{
		\includegraphics[scale=0.43]{sodb10/64_sec_pt_hist_v5.eps}
		\label{fig:s10_inc64_hist_v5}
	}
	\subfigure[PT frequency on INC128]{
		\includegraphics[scale=0.43]{sodb10/128_sec_pt_hist_v5.eps}
		\label{fig:s10_inc128_hist_v5}
	}
	\caption{PT Histograms of INC16 ... INC64~\label{fig:s10_pt_hist2}}
\end{figure}

>>>>

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC1 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/1_sec_et_hist_v5.eps}
		\label{fig:s10_inc1_et_hist_v5}
	}
	\subfigure[ET frequency on INC2 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/2_sec_et_hist_v5.eps}
		\label{fig:s10_inc2_et_hist_v5}
	}
	\subfigure[ET frequency on INC4 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/4_sec_et_hist_v5.eps}
		\label{fig:s10_inc4_et_hist_v5}
	}
	\subfigure[ET frequency on INC8 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/8_sec_et_hist_v5.eps}
		\label{fig:s10_inc8_et_hist_v5}
	}
	\caption{ET Histograms of INC1 ... INC8~\label{fig:s10_et_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC16 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/16_sec_et_hist_v5.eps}
		\label{fig:s10_inc16_et_hist_v5}
	}
	\subfigure[ET frequency on INC32 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/32_sec_et_hist_v5.eps}
		\label{fig:s10_inc32_et_hist_v5}
	}
	\subfigure[ET frequency on INC64 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/64_sec_et_hist_v5.eps}
		\label{fig:s10_inc64_et_hist_v5}
	}
	\subfigure[ET frequency on INC128 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/128_sec_et_hist_v5.eps}
		\label{fig:s10_inc128_et_hist_v5}
	}
	\caption{ET Histograms of INC16 ... INC128~\label{fig:s10_et_hist2}}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC1 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/1_sec_pt_hist_v5.eps}
		\label{fig:s10_inc1_hist_v5}
	}
	\subfigure[PT frequency on INC2 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/2_sec_pt_hist_v5.eps}
		\label{fig:s10_inc2_hist_v5}
	}
	\subfigure[PT frequency on INC4 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/4_sec_pt_hist_v5.eps}
		\label{fig:s10_inc4_hist_v5}
	}
	\subfigure[PT frequency on INC8 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/8_sec_pt_hist_v5.eps}
		\label{fig:s10_inc8_hist_v5}
	}
	\caption{PT Histograms of INC1 ... INC8~\label{fig:s10_pt_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC16 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/16_sec_pt_hist_v5.eps}
		\label{fig:s10_inc16_hist_v5}
	}
	\subfigure[PT frequency on INC32 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/32_sec_pt_hist_v5.eps}
		\label{fig:s10_inc32_hist_v5}
	}
	\subfigure[PT frequency on INC64 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/64_sec_pt_hist_v5.eps}
		\label{fig:s10_inc64_hist_v5}
	}
	\subfigure[PT frequency on INC128 on {\tt sodb10}]{
		\includegraphics[scale=0.43]{sodb10/128_sec_pt_hist_v5.eps}
		\label{fig:s10_inc128_hist_v5}
	}
	\caption{PT Histograms of INC16 ... INC64~\label{fig:s10_pt_hist2}}
\end{figure}

### 2018-05-04 pt_characterization/machine_cons_check/sodb12/res.tex
Ricks comment applied

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC1]{
		\includegraphics[scale=0.43]{sodb12/1_sec_et_hist_v5.eps}
		\label{fig:s12_inc1_et_hist_v5}
	}
	\subfigure[ET frequency on INC2]{
		\includegraphics[scale=0.43]{sodb12/2_sec_et_hist_v5.eps}
		\label{fig:s12_inc2_et_hist_v5}
	}
	\subfigure[ET frequency on INC4]{
		\includegraphics[scale=0.43]{sodb12/4_sec_et_hist_v5.eps}
		\label{fig:s12_inc4_et_hist_v5}
	}
	\subfigure[ET frequency on INC8]{
		\includegraphics[scale=0.43]{sodb12/8_sec_et_hist_v5.eps}
		\label{fig:s12_inc8_et_hist_v5}
	}
	\caption{ET Histograms of INC1 ... INC8~\label{fig:s12_et_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC16]{
		\includegraphics[scale=0.43]{sodb12/16_sec_et_hist_v5.eps}
		\label{fig:s12_inc16_et_hist_v5}
	}
	\subfigure[ET frequency on INC32]{
		\includegraphics[scale=0.43]{sodb12/32_sec_et_hist_v5.eps}
		\label{fig:s12_inc32_et_hist_v5}
	}
	\subfigure[ET frequency on INC64]{
		\includegraphics[scale=0.43]{sodb12/64_sec_et_hist_v5.eps}
		\label{fig:s12_inc64_et_hist_v5}
	}
	\subfigure[ET frequency on INC128]{
		\includegraphics[scale=0.43]{sodb12/128_sec_et_hist_v5.eps}
		\label{fig:s12_inc128_et_hist_v5}
	}
	\caption{ET Histograms of INC16 ... INC128~\label{fig:s12_et_hist2}}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC1]{
		\includegraphics[scale=0.43]{sodb12/1_sec_pt_hist_v5.eps}
		\label{fig:s12_inc1_hist_v5}
	}
	\subfigure[PT frequency on INC2]{
		\includegraphics[scale=0.43]{sodb12/2_sec_pt_hist_v5.eps}
		\label{fig:s12_inc2_hist_v5}
	}
	\subfigure[PT frequency on INC4]{
		\includegraphics[scale=0.43]{sodb12/4_sec_pt_hist_v5.eps}
		\label{fig:s12_inc4_hist_v5}
	}
	\subfigure[PT frequency on INC8]{
		\includegraphics[scale=0.43]{sodb12/8_sec_pt_hist_v5.eps}
		\label{fig:s12_inc8_hist_v5}
	}
	\caption{PT Histograms of INC1 ... INC8~\label{fig:s12_pt_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC16]{
		\includegraphics[scale=0.43]{sodb12/16_sec_pt_hist_v5.eps}
		\label{fig:s12_inc16_hist_v5}
	}
	\subfigure[PT frequency on INC32]{
		\includegraphics[scale=0.43]{sodb12/32_sec_pt_hist_v5.eps}
		\label{fig:s12_inc32_hist_v5}
	}
	\subfigure[PT frequency on INC64]{
		\includegraphics[scale=0.43]{sodb12/64_sec_pt_hist_v5.eps}
		\label{fig:s12_inc64_hist_v5}
	}
	\subfigure[PT frequency on INC128]{
		\includegraphics[scale=0.43]{sodb12/128_sec_pt_hist_v5.eps}
		\label{fig:s12_inc128_hist_v5}
	}
	\caption{PT Histograms of INC16 ... INC64~\label{fig:s12_pt_hist2}}
\end{figure}

>>>>

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC1 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/1_sec_et_hist_v5.eps}
		\label{fig:s12_inc1_et_hist_v5}
	}
	\subfigure[ET frequency on INC2 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/2_sec_et_hist_v5.eps}
		\label{fig:s12_inc2_et_hist_v5}
	}
	\subfigure[ET frequency on INC4 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/4_sec_et_hist_v5.eps}
		\label{fig:s12_inc4_et_hist_v5}
	}
	\subfigure[ET frequency on INC8 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/8_sec_et_hist_v5.eps}
		\label{fig:s12_inc8_et_hist_v5}
	}
	\caption{ET Histograms of INC1 ... INC8~\label{fig:s12_et_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC16 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/16_sec_et_hist_v5.eps}
		\label{fig:s12_inc16_et_hist_v5}
	}
	\subfigure[ET frequency on INC32 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/32_sec_et_hist_v5.eps}
		\label{fig:s12_inc32_et_hist_v5}
	}
	\subfigure[ET frequency on INC64 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/64_sec_et_hist_v5.eps}
		\label{fig:s12_inc64_et_hist_v5}
	}
	\subfigure[ET frequency on INC128 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/128_sec_et_hist_v5.eps}
		\label{fig:s12_inc128_et_hist_v5}
	}
	\caption{ET Histograms of INC16 ... INC128~\label{fig:s12_et_hist2}}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC1 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/1_sec_pt_hist_v5.eps}
		\label{fig:s12_inc1_hist_v5}
	}
	\subfigure[PT frequency on INC2 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/2_sec_pt_hist_v5.eps}
		\label{fig:s12_inc2_hist_v5}
	}
	\subfigure[PT frequency on INC4 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/4_sec_pt_hist_v5.eps}
		\label{fig:s12_inc4_hist_v5}
	}
	\subfigure[PT frequency on INC8 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/8_sec_pt_hist_v5.eps}
		\label{fig:s12_inc8_hist_v5}
	}
	\caption{PT Histograms of INC1 ... INC8~\label{fig:s12_pt_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC16 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/16_sec_pt_hist_v5.eps}
		\label{fig:s12_inc16_hist_v5}
	}
	\subfigure[PT frequency on INC32 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/32_sec_pt_hist_v5.eps}
		\label{fig:s12_inc32_hist_v5}
	}
	\subfigure[PT frequency on INC64 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/64_sec_pt_hist_v5.eps}
		\label{fig:s12_inc64_hist_v5}
	}
	\subfigure[PT frequency on INC128 on {\tt sodb12}]{
		\includegraphics[scale=0.43]{sodb12/128_sec_pt_hist_v5.eps}
		\label{fig:s12_inc128_hist_v5}
	}
	\caption{PT Histograms of INC16 ... INC64~\label{fig:s12_pt_hist2}}
\end{figure}

### 2018-05-04 pt_characterization/machine_cons_check/sodb8/res.tex
Ricks comment applied

\begin{figure}[h]
	\centering
	\subfigure[ET frequency on INC1]{
		\includegraphics[scale=0.43]{sodb8/1_sec_et_hist_v5.eps}
		\label{fig:inc1_et_hist_v5}
	}
	\subfigure[ET frequency on INC2]{
		\includegraphics[scale=0.43]{sodb8/2_sec_et_hist_v5.eps}
		\label{fig:inc2_et_hist_v5}
	}
	\subfigure[ET frequency on INC4]{
		\includegraphics[scale=0.43]{sodb8/4_sec_et_hist_v5.eps}
		\label{fig:inc4_et_hist_v5}
	}
	\subfigure[ET frequency on INC8]{
		\includegraphics[scale=0.43]{sodb8/8_sec_et_hist_v5.eps}
		\label{fig:inc8_et_hist_v5}
	}
	\caption{ET Histograms of INC1 ... INC8~\label{fig:s8_et_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC16]{
		\includegraphics[scale=0.43]{sodb8/16_sec_et_hist_v5.eps}
		\label{fig:inc16_et_hist_v5}
	}
	\subfigure[ET frequency on INC32]{
		\includegraphics[scale=0.43]{sodb8/32_sec_et_hist_v5.eps}
		\label{fig:inc32_et_hist_v5}
	}
	\subfigure[ET frequency on INC64]{
		\includegraphics[scale=0.43]{sodb8/64_sec_et_hist_v5.eps}
		\label{fig:inc64_et_hist_v5}
	}
	\subfigure[ET frequency on INC128]{
		\includegraphics[scale=0.43]{sodb8/128_sec_et_hist_v5.eps}
		\label{fig:inc128_et_hist_v5}
	}
	\caption{ET Histograms of INC16 ... INC128~\label{fig:s8_et_hist2}}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC1]{
		\includegraphics[scale=0.43]{sodb8/1_sec_pt_hist_v5.eps}
		\label{fig:inc1_hist_v5}
	}
	\subfigure[PT frequency on INC2]{
		\includegraphics[scale=0.43]{sodb8/2_sec_pt_hist_v5.eps}
		\label{fig:inc2_hist_v5}
	}
	\subfigure[PT frequency on INC4]{
		\includegraphics[scale=0.43]{sodb8/4_sec_pt_hist_v5.eps}
		\label{fig:inc4_hist_v5}
	}
	\subfigure[PT frequency on INC8]{
		\includegraphics[scale=0.43]{sodb8/8_sec_pt_hist_v5.eps}
		\label{fig:inc8_hist_v5}
	}
	\caption{PT Histograms of INC1 ... INC8~\label{fig:s8_pt_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC16]{
		\includegraphics[scale=0.43]{sodb8/16_sec_pt_hist_v5.eps}
		\label{fig:inc16_hist_v5}
	}
	\subfigure[PT frequency on INC32]{
		\includegraphics[scale=0.43]{sodb8/32_sec_pt_hist_v5.eps}
		\label{fig:inc32_hist_v5}
	}
	\subfigure[PT frequency on INC64]{
		\includegraphics[scale=0.43]{sodb8/64_sec_pt_hist_v5.eps}
		\label{fig:inc64_hist_v5}
	}
	\subfigure[PT frequency on INC128]{
		\includegraphics[scale=0.43]{sodb8/128_sec_pt_hist_v5.eps}
		\label{fig:inc128_hist_v5}
	}
	\caption{PT Histograms of INC16 ... INC64~\label{fig:s8_pt_hist2}}
\end{figure}

>>>>

\begin{figure}[h]
	\centering
	\subfigure[ET frequency on INC1 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/1_sec_et_hist_v5.eps}
		\label{fig:inc1_et_hist_v5}
	}
	\subfigure[ET frequency on INC2 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/2_sec_et_hist_v5.eps}
		\label{fig:inc2_et_hist_v5}
	}
	\subfigure[ET frequency on INC4 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/4_sec_et_hist_v5.eps}
		\label{fig:inc4_et_hist_v5}
	}
	\subfigure[ET frequency on INC8 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/8_sec_et_hist_v5.eps}
		\label{fig:inc8_et_hist_v5}
	}
	\caption{ET Histograms of INC1 ... INC8~\label{fig:s8_et_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[ET frequency on INC16 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/16_sec_et_hist_v5.eps}
		\label{fig:inc16_et_hist_v5}
	}
	\subfigure[ET frequency on INC32 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/32_sec_et_hist_v5.eps}
		\label{fig:inc32_et_hist_v5}
	}
	\subfigure[ET frequency on INC64 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/64_sec_et_hist_v5.eps}
		\label{fig:inc64_et_hist_v5}
	}
	\subfigure[ET frequency on INC128 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/128_sec_et_hist_v5.eps}
		\label{fig:inc128_et_hist_v5}
	}
	\caption{ET Histograms of INC16 ... INC128~\label{fig:s8_et_hist2}}
\end{figure}

@@

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC1 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/1_sec_pt_hist_v5.eps}
		\label{fig:inc1_hist_v5}
	}
	\subfigure[PT frequency on INC2 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/2_sec_pt_hist_v5.eps}
		\label{fig:inc2_hist_v5}
	}
	\subfigure[PT frequency on INC4 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/4_sec_pt_hist_v5.eps}
		\label{fig:inc4_hist_v5}
	}
	\subfigure[PT frequency on INC8 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/8_sec_pt_hist_v5.eps}
		\label{fig:inc8_hist_v5}
	}
	\caption{PT Histograms of INC1 ... INC8~\label{fig:s8_pt_hist1}}
\end{figure}

\begin{figure}[hp!]
	\centering
	\subfigure[PT frequency on INC16 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/16_sec_pt_hist_v5.eps}
		\label{fig:inc16_hist_v5}
	}
	\subfigure[PT frequency on INC32 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/32_sec_pt_hist_v5.eps}
		\label{fig:inc32_hist_v5}
	}
	\subfigure[PT frequency on INC64 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/64_sec_pt_hist_v5.eps}
		\label{fig:inc64_hist_v5}
	}
	\subfigure[PT frequency on INC128 on {\tt sodb8}]{
		\includegraphics[scale=0.43]{sodb8/128_sec_pt_hist_v5.eps}
		\label{fig:inc128_hist_v5}
	}
	\caption{PT Histograms of INC16 ... INC64~\label{fig:s8_pt_hist2}}
\end{figure}
